
```{r , include=FALSE}
library(readr)
library(ggplot2)
library(glmulti)
library(ggpubr)
library(ggstatsplot)
library(lme4)
library(DHARMa)
library(sjPlot)
library(svglite)
library(glmmTMB)
library(lme4)
library(MuMIn)
library(glmulti)
library(MASS)
library(ggridges)
library(lmtest)
library(dplyr)
library(patchwork)
library(survival)

load("data_1.RData")
load(file="DonorSpontaneous.RData")
load(file="DonorTransmitted.RData")
```

```{r,echo=FALSE,message=FALSE,warning=FALSE}
# Set so that long lines in R will be wrapped:
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=80), tidy=TRUE)
```

# Model analysis of the parameters influencing the number of buds produced during the study 

## Transmissible tumors dataset

### Global model selection

```{r}
donor_transN <- subset(donor_trans, donor_trans$abnormalities=="Normal")

models<- glmulti(buds_10~donor*donor_status*receiver*diff_maxR*Tumors, 
                 data=donor_transN, 
                 level = 2, method = 'h', crit='aicc',fitfunction = 'lm')

tmp <- weightable(models)
tmp2 <- tmp[tmp$aicc <= min(tmp$aicc) + 2,]
tmp2

best_rt1 <- lm(buds_10 ~ 1 + donor + donor_status + receiver + Tumors + diff_maxR + 
                 receiver:donor_status + Tumors:receiver + Tumors:diff_maxR, 
               data=donor_transN)

best_rt2 <- lm(buds_10 ~ 1 + donor + donor_status + receiver + Tumors + diff_maxR + 
                 receiver:donor_status + Tumors:donor_status + Tumors:receiver, 
               data=donor_transN)

best_rt3 <- lm(buds_10 ~ 1 + donor + donor_status + receiver + Tumors + diff_maxR + 
                 receiver:donor_status + Tumors:donor_status + Tumors:receiver + Tumors:diff_maxR, 
               data=donor_transN)

best_rt4 <- lm(buds_10 ~ 1 + donor + donor_status + receiver + Tumors + diff_maxR + 
                 donor_status:donor + receiver:donor_status + Tumors:receiver + Tumors:diff_maxR, 
               data=donor_transN)

best_rt5 <- lm(buds_10 ~ 1 + donor + donor_status + receiver + Tumors + diff_maxR + 
                 receiver:donor_status + Tumors:receiver, 
               data=donor_transN)

best_rt6 <- lm(buds_10 ~ 1 + donor + donor_status + receiver + Tumors + diff_maxR + 
                 receiver:donor_status + Tumors:donor_status + Tumors:receiver + donor:diff_maxR, 
               data=donor_transN)

tab_model(best_rt1,best_rt2,best_rt3,best_rt4,best_rt5,best_rt6, show.intercept = F)

simulateResiduals(best_rt5, plot=T)
```

\
It seems than the appearance of tumors in certain receiver, and the interaction of recipient and donor status are the factor influencing the most the number of buds produced.
\
However the number of tentacles seems also to play a role than cannont be ruled out. In order to refocus the analysis on the parameters of our interest, we will create groups of donor and recipient, in the purpose of analyzing the general relationship between tentacles number and budding at the intra-group level.

### Intra-group analysis

```{r}
donor_transN$groupDR <- paste0(donor_transN$donor, donor_transN$donor_status, donor_transN$receiver)

best_rt10.4 <- lmer(buds_10 ~ 1 + diff_maxR * Tumors + (1|groupDR), 
                    data=donor_transN)
best_rt10.3 <- lmer(buds_10 ~ 1 + diff_maxR + Tumors + (1|groupDR), 
                    data=donor_transN)
best_rt10.2 <- lmer(buds_10 ~ 1 + diff_maxR + (1|groupDR), 
                    data=donor_transN)
best_rt10.1 <- lmer(buds_10 ~ 1 + Tumors + (1|groupDR), 
                    data=donor_transN)
best_rt10.0 <- lmer(buds_10 ~ 1 + (1|groupDR), 
                    data=donor_transN)

AICc(best_rt10.4, best_rt10.3,best_rt10.2, best_rt10.1, best_rt10.0)
```
\

#### Table of the results of the best fitted models (lower AICc+2)

```{r, echo = F}

tab_model(best_rt10.4, best_rt10.3,best_rt10.2, best_rt10.1, best_rt10.0, show.intercept = F)
```

```{r, warning=F, error=FALSE, results='hide'}
simulateResiduals(best_rt10.4, plot=T)
```
\
Final model results:

```{r}
tab_model(best_rt10.4, show.intercept = F)
```

If we look at the intra group level, the number of supernumerary tentacles and the presence of tumors interact in a significant way to explain the budding rate.
\

### When does this relationship establish ?

```{r}
best_rt10 <- lmer(buds_10 ~ 1 + tenta_10 * Tumors + (1|groupDR), 
                  data=donor_transN)
best_rt9 <- lmer(buds_9 ~ 1 + tenta_9 * Tumors + (1|groupDR), 
                 data=donor_transN)
best_rt8 <- lmer(buds_8 ~ 1 + tenta_8 * Tumors + (1|groupDR), 
                 data=donor_transN)
best_rt7 <- lmer(buds_7 ~ 1 + tenta_7 * Tumors + (1|groupDR), 
                 data=donor_transN)
best_rt6 <- lmer(buds_6 ~ 1 + tenta_6 * Tumors + (1|groupDR), 
                 data=donor_transN)
best_rt5 <- lmer(buds_5 ~ 1 + tenta_5 * Tumors + (1|groupDR), 
                 data=donor_transN)
best_rt4 <- lmer(buds_4 ~ 1 + tenta_4 * Tumors+ (1|groupDR), 
                 data=donor_transN)
best_rt3 <- lmer(buds_3 ~ 1 + tenta_3 * Tumors + (1|groupDR), 
                 data=donor_transN)
best_rt2 <- lmer(buds_2 ~ 1 + tenta_2 * Tumors + (1|groupDR), 
                 data=donor_transN)
best_rt1 <- lmer(buds_1 ~ 1 + tenta_1 * Tumors + (1|groupDR), 
                 data=donor_transN)
tab_model(best_rt10,best_rt9,best_rt8,best_rt7,best_rt6,best_rt5,best_rt4,best_rt3,best_rt2,best_rt1, show.intercept = F)
```

\
The relationship between the number of tentacles, the tumor presence and the budding seems to appear only after the third week, which correspond to the establishment of the tumorous phenotype and the increase in the number of tentacles.
\
## Spontaneaous tumors dataset

### Global model

```{r}
donor_spontN <- subset(donor_spont, donor_spont$abnormalities=="Normal")

models<- glmulti(buds_10~donor*donor_status*receiver*diff_maxR*Tumors, 
                 data=donor_spontN, 
                 level = 2, method = 'h', crit='aicc',fitfunction = 'lm')

tmp <- weightable(models)
tmp2 <- tmp[tmp$aicc <= min(tmp$aicc) + 2,]
tmp2

best_rt1 <- lm(buds_10 ~ 1 + donor + receiver + Tumors + diff_maxR + 
                 receiver:donor + Tumors:donor + donor_status:diff_maxR, 
                     data=donor_spontN)

best_rt2 <- lm(buds_10 ~ 1 + donor + receiver + Tumors + diff_maxR + 
                 receiver:donor + Tumors:donor + donor_status:diff_maxR + 
                 receiver:diff_maxR, 
              data=donor_spontN)

best_rt3 <- lm(buds_10 ~ 1 + donor + receiver + diff_maxR + 
                 receiver:donor + donor:diff_maxR + donor_status:diff_maxR,
              data=donor_spontN)

best_rt4 <- lm(buds_10 ~ 1 + donor + donor_status + receiver + Tumors + diff_maxR + 
                 receiver:donor + Tumors:donor + donor_status:diff_maxR,
              data=donor_spontN)

best_rt5 <- lm(buds_10 ~ 1 + donor + donor_status + receiver + diff_maxR + 
                 receiver:donor + donor:diff_maxR + donor_status:diff_maxR, 
              data=donor_spontN)

best_rt6 <- lm(buds_10 ~ 1 + donor + receiver + Tumors + diff_maxR + 
                 receiver:donor + Tumors:donor + donor_status:diff_maxR + Tumors:diff_maxR, 
              data=donor_spontN)

best_rt7 <- lm(buds_10 ~ 1 + donor + receiver + Tumors + diff_maxR + 
                 receiver:donor + Tumors:donor + donor_status:diff_maxR + Tumors:diff_maxR, 
               data=donor_spontN)

best_rt8 <- lm(buds_10 ~ 1 + donor + donor_status + receiver + Tumors + diff_maxR + 
                 donor_status:donor + receiver:donor + Tumors:donor + donor_status:diff_maxR, 
               data=donor_spontN)
best_rt9 <- lm(buds_10 ~ 1 + donor + receiver + Tumors + diff_maxR + 
                 receiver:donor + Tumors:donor + donor:diff_maxR + donor_status:diff_maxR, 
               data=donor_spontN)

tab_model(best_rt1,best_rt2,best_rt3,best_rt4,best_rt5,best_rt6,best_rt7,best_rt8,best_rt9, show.intercept = F)

simulateResiduals(best_rt5, plot=T)
```
\
It seems than the appearance of tumors in certain donor, and the interaction of recipient and donor are the factor influencing the most the number of buds, the number of tentacles seems also to play a role when the donor was tumorous. In order to refocus the analysis on the parameters of our interest, we will create groups of donor and recipient.

### Intra group analysis

```{r}
best_rt10.4 <- lmer(buds_10 ~ 1 + diff_maxR * Tumors + (1|groupDR), 
                  data=donor_spontN)
best_rt10.3 <- lmer(buds_10 ~ 1 + diff_maxR + Tumors + (1|groupDR), 
                  data=donor_spontN)
best_rt10.2 <- lmer(buds_10 ~ 1 + diff_maxR + (1|groupDR), 
                  data=donor_spontN)
best_rt10.1 <- lmer(buds_10 ~ 1 + Tumors + (1|groupDR), 
                  data=donor_spontN)
best_rt10.0 <- lmer(buds_10 ~ 1 + (1|groupDR), 
                    data=donor_spontN)

AICc(best_rt10.4, best_rt10.3,best_rt10.2, best_rt10.1, best_rt10.0)

```

#### Table of the results of the best fitted models (lower AICc+2)

```{r, echo = F}
tab_model(best_rt10.4, best_rt10.3,best_rt10.2, best_rt10.1, best_rt10.0, show.intercept = F)
```

```{r, results='hide', echo=FALSE}
simulateResiduals(best_rt10.4, plot=T)
```

```{r}
tab_model(best_rt10.4, show.intercept = F)
```

If we look at the intra group level, there is no clear relationship. Which is quite expected given the absence of increased number of tentacles when the donor was a spontaneous tumors.

### When does this relationship establish ?

```{r}
best_rt10 <- lmer(buds_10 ~ 1 + tenta_10 * Tumors + (1|groupDR), 
                 data=donor_spontN)
best_rt9 <- lmer(buds_9 ~ 1 + tenta_9 * Tumors + (1|groupDR), 
                 data=donor_spontN)
best_rt8 <- lmer(buds_8 ~ 1 + tenta_8 * Tumors + (1|groupDR), 
                 data=donor_spontN)
best_rt7 <- lmer(buds_7 ~ 1 + tenta_7 * Tumors + (1|groupDR), 
                 data=donor_spontN)
best_rt6 <- lmer(buds_6 ~ 1 + tenta_6 * Tumors + (1|groupDR), 
                 data=donor_spontN)
best_rt5 <- lmer(buds_5 ~ 1 + tenta_5 * Tumors + (1|groupDR), 
                 data=donor_spontN)
best_rt4 <- lmer(buds_4 ~ 1 + tenta_4 * Tumors+ (1|groupDR), 
                 data=donor_spontN)
best_rt3 <- lmer(buds_3 ~ 1 + tenta_3 * Tumors + (1|groupDR), 
                 data=donor_spontN)
best_rt2 <- lmer(buds_2 ~ 1 + tenta_2 * Tumors + (1|groupDR), 
                 data=donor_spontN)
best_rt1 <- lmer(buds_1 ~ 1 + tenta_1 * Tumors + (1|groupDR), 
                 data=donor_spontN)

tab_model(best_rt10,best_rt9,best_rt8,best_rt7,best_rt6,best_rt5,best_rt4,best_rt3,best_rt2,best_rt1, show.intercept = F)
```

This is coherent, no relationship because of not enough variations.

## Global dataset, spontaneous and transmissible tumors together

### Intra group analysis

```{r}
data_1$groupDR <- as.factor(paste0(data_1$donor, data_1$donor_status, data_1$recipient))
summary(data_1$groupDR)
data_1N <- subset(data_1, data_1$abnormalities=="Normal")

best_rt10.4 <- lmer(buds_10 ~ 1 + diff_maxR * Tumors + (1|groupDR), 
                    data=donor_transN)
best_rt10.3 <- lmer(buds_10 ~ 1 + diff_maxR + Tumors + (1|groupDR), 
                    data=donor_transN)
best_rt10.2 <- lmer(buds_10 ~ 1 + diff_maxR + (1|groupDR), 
                    data=donor_transN)
best_rt10.1 <- lmer(buds_10 ~ 1 + Tumors + (1|groupDR), 
                    data=donor_transN)
best_rt10.0 <- lmer(buds_10 ~ 1 + Tumors + (1|groupDR), 
                    data=donor_transN)

AICc(best_rt10.4, best_rt10.3,best_rt10.2, best_rt10.1, best_rt10.0)
```

#### Table of the results of the best fitted models (lower AICc+2)

```{r, echo=FALSE}
tab_model(best_rt10.4, best_rt10.3,best_rt10.2, best_rt10.1, best_rt10.0, show.intercept = F)
```

The combination of increased number of tentacles and tumor presence explains a significant part of the budding rate experienced intra group.

```{r, results='hide', echo=FALSE}
simulateResiduals(best_rt10.4, plot=T)
```

### When does this relationship establish ?

```{r, echo=FALSE}
best_rt10 <- lmer(buds_10 ~ 1 + tenta_10 * Tumors + (1|groupDR), 
                  data=data_1N)
best_rt9 <- lmer(buds_9 ~ 1 + tenta_9 * Tumors+ (1|groupDR), 
                 data=data_1N)
best_rt8 <- lmer(buds_8 ~ 1 + tenta_8 * Tumors+ (1|groupDR), 
                 data=data_1N)
best_rt7 <- lmer(buds_7 ~ 1 + tenta_7 * Tumors+ (1|groupDR), 
                 data=data_1N)
best_rt6 <- lmer(buds_6 ~ 1 + tenta_6 * Tumors+ (1|groupDR), 
                 data=data_1N)
best_rt5 <- lmer(buds_5 ~ 1 + tenta_5 * Tumors+ (1|groupDR), 
                 data=data_1N)
best_rt4 <- lmer(buds_4 ~ 1 + tenta_4 * Tumors+ (1|groupDR), 
                 data=data_1N)
best_rt3 <- lmer(buds_3 ~ 1 + tenta_3 * Tumors+ (1|groupDR), 
                 data=data_1N)
best_rt2 <- lmer(buds_2 ~ 1 + tenta_2 * Tumors+ (1|groupDR), 
                 data=data_1N)
best_rt1 <- lmer(buds_1 ~ 1 + tenta_1 * Tumors+ (1|groupDR), 
                 data=data_1N)

tab_model(best_rt10,best_rt9,best_rt8,best_rt7,best_rt6,best_rt5,best_rt4,best_rt3,best_rt2,best_rt1, 
          show.intercept = F)
simulateResiduals(best_rt10, plot=T)
```

Again very coherent results, the relationship starts when the tumorous phenotype, including supernumerary tentacles is expressed.

```{r, echo=FALSE}
best_rt10.1 <- lmer(buds_10 ~ 1 + tenta_10 * Tumors + (1|groupDR), 
                  data=data_1N)
best_rt10.2 <- lmer(buds_10 ~ 1 + tenta_10 + Tumors + (1|groupDR), 
                  data=data_1N)
best_rt10.3 <- lmer(buds_10 ~ 1 + tenta_10  + (1|groupDR), 
                  data=data_1N)
best_rt10.4 <- lmer(buds_10 ~ 1 + Tumors  + (1|groupDR), 
                  data=data_1N)
best_rt10.5 <- lmer(buds_10 ~ 1 + 0  + (1|groupDR), 
                  data=data_1N)
AICc(best_rt10.1 , best_rt10.2, best_rt10.3, best_rt10.4, best_rt10.5)

tab_model(best_rt10.1, best_rt10.4,
          show.intercept = F)
```

The relationship between direct number of tentcales at the week 10 and budding rate is even stronger, however we prefer to keep consistent indicator into the final analysis.

## Data visualisation

```{r, echo = FALSE, warning=FALSE}
ggplot(data = data_1N, aes(x = diff_maxR, y = buds_10, color = Tumors)) +
  geom_point(size = 3, alpha = 0.7, position = "jitter") +  # Ajuster la taille et la transparence des points
  geom_smooth(method = "lm", se = T) + # Ajuster la régression linéaire+ 
  theme_minimal() +  # Choisir un thème minimal
  labs(title = "",
       x = "Number of supernumerary tentacles",
       y = "Number of buds produced (ten weeks)") +  # Ajouter des étiquettes d'axes
  scale_color_manual(values = c("Chartreuse4", "darkred")) +  # Changer les couleurs manuellement
  theme(legend.position = "top")+
  scale_x_continuous(breaks = seq(-1, 9, by = 2))
```
