```{r , include=FALSE}
library(readr)
library(ggplot2)
library(glmulti)
library(ggpubr)
library(ggstatsplot)
library(lme4)
library(DHARMa)
library(sjPlot)
library(svglite)
library(glmmTMB)
library(lme4)
library(MuMIn)
library(glmulti)
library(MASS)
library(ggridges)
library(lmtest)
library(dplyr)
library(patchwork)
library(survival)
library(modelsummary)

load("data_1.RData")
load(file="DonorSpontaneous.RData")
load(file="DonorTransmitted.RData")
```

# Analysis of the mortality after grafting 

## Transmissible tumors dataset

### Random effects selection (according to _Zuur et al. 2009_)

```{r Death model -random selection, echo=TRUE, warning=FALSE, width= 2}
mr1 <- glmmTMB(data=donor_trans, Death ~ donor * donor_status + receiver + (1|lot) + (1|date_draft), family = binomial, REML = T)
mr2 <- glmmTMB(data=donor_trans, Death ~ donor * donor_status + receiver + (1|date_draft/lot), family = binomial, REML = T)
mr3 <- glmmTMB(data=donor_trans, Death ~ donor * donor_status + receiver + (1|lot), family = binomial, REML = T)
mr4 <- glmmTMB(data=donor_trans, Death ~ donor * donor_status + receiver + (1|date_draft), family = binomial, REML = T)
mr5 <- glmmTMB(data=donor_trans, Death ~ donor * donor_status + receiver, family = binomial, REML = T)

AICc(mr1, mr2, mr3, mr4, mr5) 
```

There is no need to include any of the potential random effects that have been measured.

### Fixed effects selection

```{r}

m1 <- glmmTMB(data=donor_trans, Death ~ donor * donor_status * receiver+ (1|date_draft), family = binomial, REML = F)
m2 <- glmmTMB(data=donor_trans, Death ~ donor * donor_status + receiver+ (1|date_draft), family = binomial, REML = F)
m3 <- glmmTMB(data=donor_trans, Death ~ donor + donor_status * receiver+ (1|date_draft), family = binomial, REML = F)
m4 <- glmmTMB(data=donor_trans, Death ~ donor * receiver + donor_status+ (1|date_draft), family = binomial, REML = F)

m5 <- glmmTMB(data=donor_trans, Death ~ donor + donor_status + receiver+ (1|date_draft), family = binomial, REML = F)
m6 <- glmmTMB(data=donor_trans, Death ~ donor + donor_status+ (1|date_draft), family = binomial, REML = F)
m7 <- glmmTMB(data=donor_trans, Death ~ donor + receiver+ (1|date_draft), family = binomial, REML = F)
m8 <- glmmTMB(data=donor_trans, Death ~ donor_status + receiver+ (1|date_draft), family = binomial, REML = F)

m9 <- glmmTMB(data=donor_trans, Death ~ donor * donor_status+ (1|date_draft), family = binomial, REML = F)
m10 <- glmmTMB(data=donor_trans, Death ~ donor * receiver+ (1|date_draft), family = binomial, REML = F)
m11 <- glmmTMB(data=donor_trans, Death ~ donor_status * receiver+ (1|date_draft), family = binomial, REML = F)

m12 <- glmmTMB(data=donor_trans, Death ~ donor+ (1|date_draft), family = binomial, REML = F)
m13 <- glmmTMB(data=donor_trans, Death ~ donor_status+ (1|date_draft), family = binomial, REML = F)
m14 <- glmmTMB(data=donor_trans, Death ~ receiver+ (1|date_draft), family = binomial, REML = F)

m15 <- glmmTMB(data=donor_trans, Death ~ 1+ (1|date_draft), family = binomial, REML = F)

AICc(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11, m12, m13, m14, m15)
```

#### Table of the results of the best fitted models (lower AICc+2)

```{r, echo = F}
tab_model(m3, m10,show.intercept = F, show.r2 = F,show.re.var = F)
```

```{r, echo = F, results='hide'}
simulateResiduals(m10, plot=T, refit=F)
```

```{r}
m10 <- glmmTMB(data=donor_trans, Death ~ donor * receiver+ (1|date_draft), family = binomial, REML = T)
tab_model(m10, show.intercept = F, show.r2 = F, show.re.var = F)
```

\
The results are quite unclear, the best fitted models are a bit incoherent so it might just indicate a lack of power for analysis.

## Spontaneaous tumors dataset

### Random effects selection

```{r}
m1 <- glmmTMB(data=donor_spont, Death ~ donor + receiver + donor_status + (1|lot) + (1|date_draft), family = binomial, REML = T)
m2 <- glmmTMB(data=donor_spont, Death ~ donor + donor_status + receiver + (1|date_draft/lot), family = binomial, REML = T)
m3 <- glmmTMB(data=donor_spont, Death ~ donor + donor_status + receiver + (1|lot), family = binomial, REML = T)
m4 <- glmmTMB(data=donor_spont, Death ~ donor + donor_status + receiver + (1|date_draft), family = binomial, REML = T)
m5 <- glmmTMB(data=donor_spont, Death ~ donor + donor_status + receiver, family = binomial, REML = T)

AICc(m1, m2, m3, m4, m5) 
```
\
There is no need to include any of the potential random effects that have been measured.

### Fixed effects selection

```{r}
m1 <- glmmTMB(data=donor_spont, Death ~ donor * donor_status * receiver, family = binomial, REML = F)
m2 <- glmmTMB(data=donor_spont, Death ~ donor * donor_status + receiver, family = binomial, REML = F)
m3 <- glmmTMB(data=donor_spont, Death ~ donor * receiver + donor_status, family = binomial, REML = F)
m4 <- glmmTMB(data=donor_spont, Death ~ donor + receiver * donor_status, family = binomial, REML = F)

m5 <- glmmTMB(data=donor_spont, Death ~ donor + donor_status + receiver, family = binomial, REML = F)

m6 <- glmmTMB(data=donor_spont, Death ~ donor + donor_status, family = binomial, REML = F)
m7 <- glmmTMB(data=donor_spont, Death ~ donor + receiver, family = binomial, REML = F)
m8 <- glmmTMB(data=donor_spont, Death ~ donor_status + receiver, family = binomial, REML = F)

m9 <- glmmTMB(data=donor_spont, Death ~ donor * donor_status, family = binomial, REML = F)
m10 <- glmmTMB(data=donor_spont, Death ~ donor * receiver, family = binomial, REML = F)
m11 <- glmmTMB(data=donor_spont, Death ~ donor_status * receiver, family = binomial, REML = F)

m12 <- glmmTMB(data=donor_spont, Death ~ donor, family = binomial, REML = F)
m13 <- glmmTMB(data=donor_spont, Death ~ donor_status, family = binomial, REML = F)
m14 <- glmmTMB(data=donor_spont, Death ~ receiver, family = binomial, REML = F)

m15 <- glmmTMB(data=donor_spont, Death ~ 1, family = binomial, REML = F)

AICc(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11, m12, m13, m14, m15)
```
\
The best model is the m10, tacking into account the donor line and the recipient line.
\

```{r, echo=F, results='hide'}
simulateResiduals(m10, plot=T)
```

```{r, echo=FALSE}
m10 <- glmmTMB(data=donor_spont, Death ~ donor * receiver, family = binomial, REML = T)
tab_model(m10, show.intercept = F, show.r2 = F, show.re.var = F) 
```

\
The Mt donor induces more mortality in the TV recipient than in the SpB recipient.

## Data visualisation

```{r, echo=F, warning=FALSE, results='hide'}
donor_trans1<- donor_trans
donor_spont1<- donor_spont
donor_trans1$donor_status <- factor(donor_trans$donor_status,
                                   levels = c("NT", "T"),
                                   labels = c("Healthy donor","Tumorous donor"))

donor_spont1$donor_status <- factor(donor_spont$donor_status,
                                   levels = c("NT", "T"),
                                   labels = c("Healthy donor","Tumorous donor"))

Table_DT <- donor_trans1 %>% count(donor, donor_status, receiver, Death, sort = F)
Table_DT <- cbind(Table_DT, pos = rep(c(0.9,0.1), 8))

Table_DS <- donor_spont1 %>% count(donor, donor_status, receiver, Death, sort = F)
Table_DS <- cbind(Table_DS, pos = c(rep(c(0.9,0.1), 5), 0.9, rep(c(0.9,0.1), 2)))

a <- ggplot(donor_trans1, aes(x = receiver, fill = Death)) +
  geom_bar(position = "fill")+
  theme_classic()+
  theme(legend.position="none")+
  scale_x_discrete(labels = c("SpB", "Wild\ngroup\n"))+
  scale_fill_manual(values=c("Grey", "black"))+
  ylab("Death rate")+
  xlab("Recipient")+
  ylim (c(0, 1.2))+
  ggtitle("Transmitted tumors\nDonor lineages\n")+
  facet_grid(cols=vars(donor), rows = vars(donor_status))+
  
  theme(title = element_text(size = 15),
        axis.title.y = element_text(size = 20),
        axis.title.x = element_text(size = 20),
        axis.text = element_text(size = 12),
        strip.text.y = element_text(size = 16),
        strip.text.x = element_text(size = 16))+
  
  geom_text(data = Table_DT,
            aes(y = pos, x=receiver, fill= Death, label = n), 
            color = "white", fontface = "bold", size=5)
  

b <- ggplot(donor_spont1, aes(x = receiver, fill = Death)) +
  geom_bar(position = "fill")+
  theme(legend.position="none")+
  facet_grid(cols=vars(donor), rows = vars(donor_status))+
  scale_x_discrete(labels = c("SpB", "Wild\ngroup\n"))+
  scale_fill_manual(values=c("Grey", "black"))+
  ylab("Death rate")+
  xlab("Recipient")+
  ylim (c(0, 1.2))+
  ggtitle("Spontaneous tumors\nDonor lineages\n")+
  theme_classic()+
  
  theme(title = element_text(size = 15),
        axis.ticks = element_blank(),
        axis.title.y = element_text(size = 20),
        axis.title.x = element_text(size = 20),
        axis.text = element_text(size = 12),
        strip.text.y = element_text(size = 16),
        strip.text.x = element_text(size = 16))+
  
  geom_text(data = Table_DS,
            aes(y = pos, x=receiver, fill= Death, label = n), 
            color = "white", fontface = "bold", size=5)
a+b
```

