
```{r , include=FALSE}
library(readr)
library(ggplot2)
library(glmulti)
library(ggpubr)
library(ggstatsplot)
library(lme4)
library(DHARMa)
library(sjPlot)
library(svglite)
library(glmmTMB)
library(lme4)
library(MuMIn)
library(glmulti)
library(MASS)
library(ggridges)
library(lmtest)
library(dplyr)
library(patchwork)
library(survival)

load("data_1.RData")
load(file="DonorSpontaneous.RData")
load(file="DonorTransmitted.RData")
```

# Analysis of the tentacules numbers of donor and recipient hydras

## Comparisions between tumorous and non-tumorous of each donor lineages
\
We calculated the differences between tumors and non-tumors within each line using Wilcox tests.
\
```{r, echo=F, warning=FALSE}
data_1$group <- as.factor(paste0(data_1$donor, data_1$donor_status))
```

```{r, echo=TRUE, warning=FALSE}
wilcox.test(data_1$donor_tentacle[data_1$group=="RobNT"], data_1$donor_tentacle[data_1$group=="RobT"])

wilcox.test(data_1$donor_tentacle[data_1$group=="SpBNT"], data_1$donor_tentacle[data_1$group=="SpBT"])
wilcox.test(data_1$donor_tentacle[data_1$group=="SpBNT"], data_1$donor_tentacle[data_1$group=="SpB_spontT"])

wilcox.test(data_1$donor_tentacle[data_1$group=="MTNT"], data_1$donor_tentacle[data_1$group=="MTT"])
```

### Graph of number of tentacles in donor lines

```{r, echo=FALSE, warning=FALSE, results='hide', message=FALSE}

data_1$group <- paste0(data_1$donor, data_1$donor_status)
data_1$group <- recode_factor(data_1$group, 
                              RobNT = "Rob\nControl",
                              RobT = "Rob\nTransmitted\nTumors",
                              
                              SpBNT = "SpB\nControl", 
                              SpBT = "SpB\nTransmitted\nTumors",
                              SpB_spontT = "SpB\nSpontaneous\nTumors",
                              
                              MTNT = "MT\nControl",
                              MTT = "MT\nSpontaneous\nTumors")

p1 <- ggbetweenstats(
  data = data_1,
  x = group, ## grouping/independent variable
  y = donor_tentacle, ## dependent variables
  plot.type = "box", ## type of plot
  pairwise.display = "none",
  point.args = list(position = ggplot2::position_jitterdodge(dodge.width = 0.9), alpha =
    0.4, size = 4, stroke = 0),
  results.subtitle = F)+
  scale_color_manual(values = c("chartreuse4","darkred",
             "chartreuse4","darkred","darkred",
             "chartreuse4","darkred"))
p1+ggplot2::ylab("Number of tentacles")+
  ggplot2::xlab("\nHydra group")
```

### Graph of number of tentacles in recipient lines

```{r, warning=FALSE, echo=FALSE, message=FALSE}
data_1$receiver <- recode_factor(data_1$receiver, 
                              SpB = "SpB\nControl",
                              TV = "Wild\nGroup")
p2 <- ggbetweenstats(
  data = data_1,
  x = receiver, ## grouping/independent variable
  y = receiver_tentacle, ## dependent variables
  pairwise.comparisons = T,
  plot.type = "box", ## type of plot
  point.args = list(position = ggplot2::position_jitterdodge(dodge.width = 0.9), alpha =
    0.4, size = 4, stroke = 0),
  type = "np",
  conf.level = 0.99,
  results.subtitle = F,
  centrality.label.args = list(size = 5, direction="both", nudge_y=17, segment.alpha = 0),
  centrality.type = "nonparametric")

p2+ggplot2::scale_color_manual(values = c("chartreuse4","chartreuse4"))+
  ggplot2::ylab("Number of tentacles")+
  ggplot2::xlab("\nHydra group")+
  ggplot2::ylim(2,9)
```

# Analysis of the variation of the number of tentacles after grafting

## Transmissible tumors dataset

### Random effects selection

```{r}
donor_trans <- subset(donor_trans, donor_trans$diff_maxR!="NA")

m1 <- glmmTMB(data=donor_trans, diff_maxR+2 ~ donor +donor_status + receiver + donor_tentacle + receiver_tentacle + (1|lot) + (1|date_draft), family = poisson, REML = T)
m2 <- glmmTMB(data=donor_trans, diff_maxR+2 ~ donor +donor_status + receiver + donor_tentacle + receiver_tentacle + (1|date_draft/lot), family = poisson, REML = T)
m3 <- glmmTMB(data=donor_trans, diff_maxR+2 ~ donor +donor_status + receiver + donor_tentacle + receiver_tentacle + (1|lot), family = poisson, REML = T)
m4 <- glmmTMB(data=donor_trans, diff_maxR+2 ~ donor +donor_status + receiver + donor_tentacle + receiver_tentacle + (1|date_draft), family = poisson, REML = T)
m5 <- glmmTMB(data=donor_trans, diff_maxR+2 ~ donor +donor_status + receiver + donor_tentacle + receiver_tentacle, family = poisson, REML = T)

AICc(m1, m2, m3, m4, m5) 
```
\
There is no need to include any of the potential random effects that have been measured.

### Fixed effects selection
\
Given the number of potential effects to evaluate, we have opted for an automatic selection of fixed effects
\

```{R, warning=F}
options(na.action = "na.omit")
mT_trans_full = glmmTMB(data=donor_trans, diff_maxR+2 ~ donor * donor_status * receiver +  receiver_tentacle + donor_tentacle, family = poisson, REML = F)
options(na.action = "na.fail")
dd2 = dredge(mT_trans_full, rank = "AICc")
```

#### Table of the results of the best fitted models (lower AICc+2)

```{r, echo=FALSE, warning=FALSE}
tab_model(get.models(dd2, subset = delta < 2), show.intercept = F, show.r2 = F,show.re.var = F)
#get.models(dd2, subset = delta < 2)
options(na.action = "na.omit")
```

```{r, warning=FALSE}
best_model_tentaTrans <- glmmTMB(data=donor_trans,diff_maxR+2 ~ donor_status + receiver_tentacle, family = poisson, REML = T)
tab_model(best_model_tentaTrans, show.intercept = F, show.r2=F)
```
\

On average, a individual who received a transplant of tumorous tissue developed 1.45 more tentacles compared to those who received healthy tissue and developed only one tentacle. Furthermore, individuals with a high number of tentacles prior to transplantation experienced a reduced increase in the number of tentacles after the procedure (IRR=0.83 [0.74 - 0.93], p=0.001), suggesting a possible threshold effect.

```{r, warning=F, error=FALSE, results='hide'}
simulateResiduals(best_model_tentaTrans, plot=T)
```
\
The model is not perfectly balanced, however changing to another family such as negative binomial or zero-truncated does not significantly enhance the quality of the models or their outcomes.

## Spontaneous tumors dataset

### Random effects selection

```{r}
donor_spont <- subset(donor_spont, donor_spont$diff_maxR!="NA")

m1 <- glmmTMB(data=donor_trans, diff_maxR+2 ~ donor + Tumors +donor_status + receiver + donor_tentacle + receiver_tentacle + (1|lot) + (1|date_draft), family = poisson, REML = T)
m2 <- glmmTMB(data=donor_trans, diff_maxR+2 ~ donor + Tumors +donor_status + receiver + donor_tentacle + receiver_tentacle + (1|date_draft/lot), family = poisson, REML = T)
m3 <- glmmTMB(data=donor_trans, diff_maxR+2 ~ donor + Tumors +donor_status + receiver + donor_tentacle + receiver_tentacle + (1|lot), family = poisson, REML = T)
m4 <- glmmTMB(data=donor_trans, diff_maxR+2 ~ donor + Tumors +donor_status + receiver + donor_tentacle + receiver_tentacle + (1|date_draft), family = poisson, REML = T)
m5 <- glmmTMB(data=donor_trans, diff_maxR+2 ~ donor + Tumors +donor_status + receiver + donor_tentacle + receiver_tentacle, family = poisson, REML = T)

AICc(m1, m2, m3, m4, m5) 
```
\
There is no need to include any of the potential random effects that have been measured.

### Fixed effects selection

\
Given the number of potential effects to evaluate, we have opted for an automatic selection of fixed effects
\

```{R, warning=F}
options(na.action = "na.omit")
mT_spont_full = glmmTMB(data=donor_spont, diff_maxR+2 ~ donor * donor_status * receiver +  receiver_tentacle +donor_tentacle, family = poisson)
options(na.action = "na.fail")
dd = dredge(mT_spont_full, rank = "AICc")
```

#### Table of the results of the best fitted models (lower AICc+2)

```{r, echo=FALSE}
tab_model(get.models(dd, subset = delta < 2), show.intercept = F, show.r2 = F,show.re.var = F)
#get.models(dd, subset = delta < 2)
options(na.action = "na.omit")
```

```{r}
best_model_tentaSpont <- glmmTMB(data=donor_spont,diff_maxR+2 ~ 1, family = poisson, REML = T)
tab_model(best_model_tentaSpont, show.intercept = F, show.r2=F)
```
\

None of the factors assessed had a notable effect on the variability of the tentacle count following transplantation within this group.

