
```{r , include=FALSE}
library(readr)
library(ggplot2)
library(glmulti)
library(ggpubr)
library(ggstatsplot)
library(lme4)
library(DHARMa)
library(sjPlot)
library(svglite)
library(glmmTMB)
library(lme4)
library(MuMIn)
library(glmulti)
library(MASS)
library(ggridges)
library(lmtest)
library(dplyr)
library(patchwork)
library(survival)

load("data_1.RData")
load(file="DonorSpontaneous.RData")
load(file="DonorTransmitted.RData")
```

```{r,echo=FALSE,message=FALSE,warning=FALSE}
# Set so that long lines in R will be wrapped:
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=80), tidy=TRUE)
```

# Analysis of the tumors development after grafting

## Transmissible tumors dataset

### Random effects selection

```{r}
m1 <- glmmTMB(data=donor_trans, Tumors ~ donor * donor_status + receiver + (1|lot) + (1|date_draft), family = binomial, REML = T)
m2 <- glmmTMB(data=donor_trans, Tumors ~ donor * donor_status + receiver + (1|date_draft/lot), family = binomial, REML = T)
m3 <- glmmTMB(data=donor_trans, Tumors ~ donor * donor_status + receiver + (1|lot), family = binomial, REML = T)
m4 <- glmmTMB(data=donor_trans, Tumors ~ donor * donor_status + receiver + (1|date_draft), family = binomial, REML = T)
m5 <- glmmTMB(data=donor_trans, Tumors ~ donor * donor_status + receiver, family = binomial, REML = T)

AICc(m1, m2, m3, m4, m5) 
```
\
There is no need to include any of the potential random effects that have been measured.

### Fixed effects selection

```{r}
m1 <- glmmTMB(data=donor_trans, Tumors ~ donor * donor_status * receiver, family = binomial, REML = F)
m2 <- glmmTMB(data=donor_trans, Tumors ~ donor * donor_status + receiver, family = binomial, REML = F)
m3 <- glmmTMB(data=donor_trans, Tumors ~ donor + donor_status * receiver, family = binomial, REML = F)
m4 <- glmmTMB(data=donor_trans, Tumors ~ donor * receiver + donor_status, family = binomial, REML = F)

m5 <- glmmTMB(data=donor_trans, Tumors ~ donor + donor_status + receiver, family = binomial, REML = F)
m6 <- glmmTMB(data=donor_trans, Tumors ~ donor + donor_status, family = binomial, REML = F)
m7 <- glmmTMB(data=donor_trans, Tumors ~ donor + receiver, family = binomial, REML = F)
m8 <- glmmTMB(data=donor_trans, Tumors ~ donor_status + receiver, family = binomial, REML = F)

m9 <- glmmTMB(data=donor_trans, Tumors ~ donor * donor_status, family = binomial, REML = F)
m10 <- glmmTMB(data=donor_trans, Tumors ~ donor * receiver, family = binomial, REML = F)
m11 <- glmmTMB(data=donor_trans, Tumors ~ donor_status * receiver, family = binomial, REML = F)

m12 <- glmmTMB(data=donor_trans, Tumors ~ donor, family = binomial, REML = F)
m13 <- glmmTMB(data=donor_trans, Tumors ~ donor_status, family = binomial, REML = F)
m14 <- glmmTMB(data=donor_trans, Tumors ~ receiver, family = binomial, REML = F)

m15 <- glmmTMB(data=donor_trans, Tumors ~ 1, family = binomial, REML = F)

AICc(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11, m12, m13, m14, m15)
```
\

#### Table of the results of the best fitted models (lower AICc+2)

```{r, echo = F}
tab_model(m9, m6,show.intercept = F, show.r2 = F,show.re.var = F)
```

```{r, warning=F, error=FALSE, results='hide'}
simulateResiduals(m9, plot=T)
```
\
Final model results:

```{r}
m9 <- glmmTMB(data=donor_trans, Tumors ~ donor * donor_status, family = binomial, REML = T)
tab_model(m9, show.intercept = F, show.r2 = F,show.re.var = F)
```

There is an slightly significant effect of the status of the donor, with individuals grafted with Robusta tissues developing less tumors than healthy one.
And a strong effect of the donor status, with 10,4 % (IRR of 9,62) more chances to develop tumors when the giver hydra is tumorous.
Maybe a small interaction but not enough power to be sure.

## Spontaneaous tumors dataset

### Random effects selection

```{r}
m1 <- glmmTMB(data=donor_spont, Tumors ~ donor + receiver + donor_status + (1|lot) + (1|date_draft), family = binomial, REML = T)
m2 <- glmmTMB(data=donor_spont, Tumors ~ donor + donor_status + receiver + (1|date_draft/lot), family = binomial, REML = T)
m3 <- glmmTMB(data=donor_spont, Tumors ~ donor + donor_status + receiver + (1|lot), family = binomial, REML = T)
m4 <- glmmTMB(data=donor_spont, Tumors ~ donor + donor_status + receiver + (1|date_draft), family = binomial, REML = T)
m5 <- glmmTMB(data=donor_spont, Tumors ~ donor + donor_status + receiver, family = binomial, REML = T)

AICc(m1, m2, m3, m4, m5) 
```
\
There is no need to include any of the potential random effects that have been measured.

### Fixed effects selection

```{r}
m1 <- glmmTMB(data=donor_spont, Tumors ~ donor * donor_status * receiver, family = binomial, REML = F)
m2 <- glmmTMB(data=donor_spont, Tumors ~ donor * donor_status + receiver, family = binomial, REML = F)
m3 <- glmmTMB(data=donor_spont, Tumors ~ donor * receiver + donor_status, family = binomial, REML = F)
m4 <- glmmTMB(data=donor_spont, Tumors ~ donor + receiver * donor_status, family = binomial, REML = F)

m5 <- glmmTMB(data=donor_spont, Tumors ~ donor + donor_status + receiver, family = binomial, REML = F)

m6 <- glmmTMB(data=donor_spont, Tumors ~ donor + donor_status, family = binomial, REML = F)
m7 <- glmmTMB(data=donor_spont, Tumors ~ donor + receiver, family = binomial, REML = F)
m8 <- glmmTMB(data=donor_spont, Tumors ~ donor_status + receiver, family = binomial, REML = F)

m9 <- glmmTMB(data=donor_spont, Tumors ~ donor * donor_status, family = binomial, REML = F)
m10 <- glmmTMB(data=donor_spont, Tumors ~ donor * receiver, family = binomial, REML = F)
m11 <- glmmTMB(data=donor_spont, Tumors ~ donor_status * receiver, family = binomial, REML = F)

m12 <- glmmTMB(data=donor_spont, Tumors ~ donor, family = binomial, REML = F)
m13 <- glmmTMB(data=donor_spont, Tumors ~ donor_status, family = binomial, REML = F)
m14 <- glmmTMB(data=donor_spont, Tumors ~ receiver, family = binomial, REML = F)

m15 <- glmmTMB(data=donor_spont, Tumors ~ 1, family = binomial, REML = F)

AICc(m1, m2, m3, m4, m5, m6, m7, m8, m9, m10, m11, m12, m13, m14, m15)
```

#### Table of the results of the best fitted models (lower AICc+2)

```{r, echo = F}
tab_model(m8, m13, m3, m4, m6, show.intercept = F, show.r2 = F,show.re.var = F) 
````

```{r, results='hide', echo=FALSE}
simulateResiduals(m8, plot=T)
````

```{r}
m13 <- glmmTMB(data=donor_spont, Tumors ~ donor_status, family = binomial, REML = T)
tab_model(m13, show.intercept = F, show.r2 = F,show.re.var = F) 
```

There is a small but significant effect of the status of the donor, the tumorous donors triggers twice and half more tumors in there grafted host.

## Data visualisation

```{r, echo = FALSE, warning=FALSE}
donor_trans$donor_status <- factor(donor_trans$donor_status,
                                   levels = c("NT", "T"),
                                   labels = c("Healthy donor","Tumorous donor"))

donor_spont$donor_status <- factor(donor_spont$donor_status,
                                   levels = c("NT", "T"),
                                   labels = c("Healthy donor","Tumorous donor"))

Table_DT <- donor_trans %>% count(donor, donor_status, receiver, Tumors, sort = F)
Table_DT <- cbind(Table_DT, pos = rep(c(0.90,0.1), 8))

Table_DS <- donor_spont %>% count(donor, donor_status, receiver, Tumors, sort = F)
Table_DS <- cbind(Table_DS, pos = rep(c(0.90,0.1), 8))

a <- ggplot(donor_trans, aes(x = receiver, fill = Tumors)) +
  geom_bar(position = "fill",alpha=0.8)+
  facet_grid(cols=vars(donor), rows = vars(donor_status))+
  scale_x_discrete(labels = c("SpB", "Wild\ngroup\n"))+
  scale_fill_manual(values=c("seagreen3", "#DC143C"))+
  ylab("Tumor development rate")+
  xlab("Recipient")+
  ylim(c(0, 1.2))+
  ggtitle("Transmitted tumors\nDonor lineages\n")+
  theme_classic()+
  theme(legend.position="none")+
  theme(title = element_text(size = 15),
        axis.title.y = element_text(size = 20),
        axis.title.x = element_text(size = 20),
        axis.text = element_text(size = 12),
        strip.text.y = element_text(size = 16),
        strip.text.x = element_text(size = 16))+
  
  geom_text(data = Table_DT,
            aes(y = pos, x=receiver, fill= Tumors, label = n), 
            color = "white", fontface = "bold", size= 5)

b <- ggplot(donor_spont, aes(x = receiver, fill = Tumors)) +
  geom_bar(position = "fill",alpha=0.8)+
  facet_grid(cols=vars(donor), rows = vars(donor_status))+
  scale_x_discrete(labels = c("SpB", "Wild\ngroup\n"))+
  scale_fill_manual(values=c("seagreen3", "#DC143C"))+
  ylab("Tumor development rate")+
  xlab("Recipient")+
  ggtitle("Spontaneous tumors\nDonor lineages\n")+
  ylim (c(0, 1.2))+
  theme_classic()+
  
  theme(title = element_text(size = 15),
        axis.title.y = element_text(size = 20),
        axis.title.x = element_text(size = 20),
        axis.text = element_text(size = 12),
        strip.text.y = element_text(size = 16),
        strip.text.x = element_text(size = 16))+
  
  geom_text(data = Table_DS,
            aes(y = pos, x=receiver, fill= Tumors, label = n),
            color = "white", fontface = "bold", size= 5)

a+b
```
